{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-29 bmvc_review.tex
EnKCF technical explanation added - KCF trimmed - PF Left
EnKCF2 Added

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed} Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while perserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure}.

\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

\begin{comment}
\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

@@

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
\label{Workflow_figure}
\end{figure*}

@@

Our MKCF based tracking framework employs different capabilities and
tasks to each correlation filter learned temporally. In
\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
\textit{target-only} area whereas \cite{henriques2015high,
  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
learned on \textit{target+background} area to find the optimal scale
in scale space. To learn the scale filter, $R_{s}$, we follow a
similar approach to \cite{ma2015long}. We believe that translation
filter needs to include background information to better discriminate
target from background, however, the goal of the scale filter is to
estimate the right size of the target, not to discriminate it from
background. Also, by using a smaller ROI we can reduce the template size
 to learn the scale filter, resulting in higher speed scale
estimation module and earning us some time to update scale. Finally, the scale filter help us on the track
re-initialization module which includes running an object proposals
algorithm to extract proposals from salient regions. By using the
scale filter in re-initialization module, we can reduce the
element-wise operations compared to the translation filters. Also, we can 
avoid false target re-initialization in the case of rapid background change as $R_{t}^{s}$ and
$R_{t}^{L}$ learn background in addition to target. The \textit{target+small background} area translation filter, $R_{t}^{S}$,
is assigned a larger template size than $R_{s}$ and smaller than
$R_{t}^{L}$. It estimates only translation similar
to \cite{henriques2015high}. Finally, the \textit{target+large
  background} area translation filter, $R_{t}^{L}$ , estimates translation of a target as $R_{t}^{S}$. We propose scale estimation at every $n$ number of frames using the scale filter. In our experiments on $OTB100$ and $UAV123$,
we observed that $n$ = 5 gives the best results in terms of precision and success overlap rates. The \textit{target+large background} translation filter is run
in the next frame after the scale filter as we want to avoid drifts which is more likely to happen running only $R_{s}$. Considering a large ROI for $R_{t}^{L}$ can degrade its performance due to information loss resulting from ROI resizing. On the other hand, only HoG features are used in $R_{t}^{S}$ as it focuses on a smaller ROI, giving us more discriminative HoG features. In our framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$. $R_{t}^{S}$, on the other hand, focuses on the shape features of the target that is not fully exploited in $R_{t}^{L}$ and $R_{t}^{S}$. For this reason, we employ \textit{HoG} features in $R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in $R_{t}^{L}$. Fig.~\ref{Workflow_figure} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

@@

WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE
POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
\section{Track Re-initilization via Re-detection}
\label{sc:Re-initialization}

@@

\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the committee of the correlation filters are important as the each correlation filter addresses the weakness of another one. For instance, $R_{t}^{L}$'s main task is to recover from the previous frame where only $R_{s}$ and particle filter's prior distribution are used to estimate scale and translation. We set the learning rates ($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$ and $0.010$. The desired response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. In our particle filter implementation, we employ $1000$ particles and use the \textit{efficient number of samples} metric shown below to determine whether we need to perform importance re-sampling or not to keep reasonable variance.
\begin{equation}
  \hat{N}_{eff} = \dfrac{1}{\sum_{i=1}^{P}(w_{p})^{2}}, 
\end{equation}
 where $w$ represents the particles' weights and re-sampling is performed only if $\hat{N}_{eff}$ is smaller than three.

\textbf{Features Selections.} We use the fast Histogram of Oriented Gradients (fHoG)\cite{felzenszwalb2010object} and Color-naming\cite{van2009learning} features to learn target and background models. $R_{t}^{L}$ uses both fHoG and color features as it covers a large ROI where fHoG features may not be reliable alone. On the other hand, $R_{t}^{S}$ is assigned only fHoG features as it covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features as it is assigned lower template size, yielding space to exploit two feature modalities.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
\label{fig:OTB100_DATASET}
\end{figure}
%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
%\end{figure}
%
%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures. }\label{fig:OTB100_DATASET}
%\end{figure}

\textbf{Overall Performance without Re-detection on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics. Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence. In precision, we rank the trackers based on the precision numbers at 20 pixels. The success rate metric evaluates the overlap between the ground truth and tracking output. The intersection-to-union ratio of two regions over the frames of one sequence. Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames. We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers. These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The E$n$KCF tracker outperforms the other methods in high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on the same dataset although it is $10$-$20$ times faster than these trackers. On the other hand, the E$n$KCF does a decent job on approximating the scale of the target in highly efficient manner. This is proved by the fact that it ranks third best tracker in terms of \textit{area under curve} (AUC) value for the success rate plot. It outperforms the high speed trackers by about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even better than most of the low speed trackers. For instance, it outperforms Struct and DSST by $5\%$ and $10\%$ while running at more than $30$ and $10$ times larger operation rate.

\textbf{Overall Performance without Re-detection on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset. Again, it performs slightly better than the high speed trackers in precision. Interestingly, it outperforms the another correlation filter based tracker, DSST while running only $5\%$ behind of another low-speed scale adaptive SAMF tracker. As in UAV123 dataset, the E$n$KCF performs exceptionally in handling the scale changes. It is ranked as the fifth best tracker while being the second highest speed tracker behind MOSSE. It performs only around $2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers prove that E$n$KCF is not only a good candidate for tracking on a UAV-based mobile platform but also mobile platforms on smart phones.

>>>>

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while perserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure_EnKCF}.

\item \textbf{More Accurate Single-Target Tracking in a Relatively Lower-Speed ( $\geq 150$ fps)} Our second algorithm, 
{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty
modified to perform more accurate in more challenging scenarios, particularly the ones with large ego-motion and object
motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a dataset (UAV123$\_$10fps) including sequences
with large ego-motion on the UAV platform. The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.

\begin{comment}\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

@@

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
\label{Workflow_figure_EnKCF}
\end{figure*}

\begin{figure*}[!t]
\centering
\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
\caption{The workflow of our EnKCF2 tracker that is more robust to large camera and fast object motion than our EnKCF tracker.}
\label{Workflow_figure_EnKCF2}
\end{figure*}

@@

Our MKCF based tracking framework employs different capabilities and
tasks to each correlation filter learned temporally. In
\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
\textit{target-only} area whereas \cite{henriques2015high,
  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
learned on \textit{target+background} area to find the optimal scale
in scale space. To learn the scale filter, $R_{s}$, we follow a
similar approach to \cite{ma2015long}. We believe that translation
filter needs to include background information to better discriminate
target from background, however, the goal of the scale filter is to
estimate the right size of the target, not to discriminate it from
background. Also, by using a smaller ROI we can reduce the template size
 to learn the scale filter, resulting in higher speed scale
estimation module and earning us some time to update scale. Finally, the scale filter help us on the track
re-initialization module which includes running an object proposals
algorithm to extract proposals from salient regions. By using the
scale filter in re-initialization module, we can reduce the
element-wise operations compared to the translation filters. Also, we can 
avoid false target re-initialization in the case of rapid background change as $R_{t}^{s}$ and
$R_{t}^{L}$ learn background in addition to target. The \textit{target+small background} area translation filter, $R_{t}^{S}$,
is assigned a larger template size than $R_{s}$ and smaller than
$R_{t}^{L}$. It estimates only translation similar
to \cite{henriques2015high}. Finally, the \textit{target+large
  background} area translation filter, $R_{t}^{L}$ , estimates translation of a target as $R_{t}^{S}$. We propose scale estimation at every $n$ number of frames using the scale filter. In our experiments on $OTB100$ and $UAV123$,
we observed that $n$ = 5 gives the best results in terms of precision and success overlap rates. The \textit{target+large background} translation filter is run
in the next frame after the scale filter as we want to avoid drifts which is more likely to happen running only $R_{s}$. Considering a large ROI for $R_{t}^{L}$ can degrade its performance due to information loss resulting from ROI resizing. On the other hand, only HoG features are used in $R_{t}^{S}$ as it focuses on a smaller ROI, giving us more discriminative HoG features. In our framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$. $R_{t}^{S}$, on the other hand, focuses on the shape features of the target that is not fully exploited in $R_{t}^{L}$ and $R_{t}^{S}$. For this reason, we employ \textit{HoG} features in $R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in $R_{t}^{L}$. Fig.~\ref{Workflow_figure_EnKCF} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

@@

@@

\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the committee of the correlation filters are important as the each correlation filter addresses the weakness of another one. For instance, $R_{t}^{L}$'s main task is to recover from the previous frame where only $R_{s}$ and particle filter's prior distribution are used to estimate scale and translation. We set the learning rates ($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$ and $0.010$. The desired response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We note that all the hyper-parameters are same for EnKCF and EnKCF2 trackers. We only set the learning rate of $R_{t}^{L}$ to $0.12$. In our particle filter implementation, we employ $1000$ particles and use the \textit{efficient number of samples} metric shown below to determine whether we need to perform importance re-sampling or not to keep reasonable variance.

\begin{equation}
  \hat{N}_{eff} = \dfrac{1}{\sum_{i=1}^{P}(w_{p})^{2}}, 
\end{equation}
 where $w$ represents the particles' weights and re-sampling is performed only if $\hat{N}_{eff}$ is smaller than three.

\textbf{Features Selections.} We use the fast Histogram of Oriented Gradients (fHoG)\cite{felzenszwalb2010object} and Color-naming\cite{van2009learning} features to learn target and background models. $R_{t}^{L}$ uses both fHoG and color features as it covers a large ROI where fHoG features may not be reliable alone. On the other hand, $R_{t}^{S}$ is assigned only fHoG features as it covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features as it is assigned lower template size, yielding space to exploit two feature modalities. We emphasize that same features are applied to the correlations filters in EnKCF and EnKCF2 trackers.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
\label{fig:OTB100_DATASET}
\end{figure}

\textbf{Overall Performance on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics. Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence. In precision, we rank the trackers based on the precision numbers at 20 pixels. The success rate metric evaluates the overlap between the ground truth and tracking output. The intersection-to-union ratio of two regions over the frames of one sequence. Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames. We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers. These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The E$n$KCF tracker outperforms the other methods in high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on the same dataset although it is $10$-$20$ times faster than these trackers. On the other hand, the E$n$KCF does a decent job on approximating the scale of the target in highly efficient manner. This is proved by the fact that it ranks third best tracker in terms of \textit{area under curve} (AUC) value for the success rate plot. It outperforms the high speed trackers by about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even better than most of the low speed trackers. For instance, it outperforms Struct and DSST by $5\%$ and $10\%$ while running at more than $30$ and $10$ times larger operation rate.

\textbf{Overall Performance on UAV123$\_$10fps Dataset.}

\textbf{Overall Performance on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset. Again, it performs slightly better than the high speed trackers in precision. Interestingly, it outperforms the another correlation filter based tracker, DSST while running only $5\%$ behind of another low-speed scale adaptive SAMF tracker. As in UAV123 dataset, the E$n$KCF performs exceptionally in handling the scale changes. It is ranked as the fifth best tracker while being the second highest speed tracker behind MOSSE. It performs only around $2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers prove that E$n$KCF is not only a good candidate for tracking on a UAV-based mobile platform but also mobile platforms on smart phones.
